DraftFunctions

### 2022-02-07 R/DraftFunctions.Rmd
Clean after 2ndTrails

>>>>

# Secondary trails in Data
```{r}
scenario <- "manual"
winching <- "2"
objective <- 10
fuel <- "2"
diversification <- TRUE

inventory <- addtreedim(cleaninventory(Paracou6_2016, PlotMask),
                        volumeparameters = ForestZoneVolumeParametersTable)

treeselectionoutputs <- suppressWarnings(treeselection(inventory,
                                                       topography = DTMParacou,
                                                       speciescriteria = SpeciesCriteria, objective = objective,
                                                       scenario = scenario, fuel = fuel,
                                                       diversification = diversification,
                                                       winching = winching, specieslax = FALSE,
                                                       objectivelax = TRUE, plotslope = HarvestableAreaOutputsCable$PlotSlope,
                                                       harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
                                                       advancedloggingparameters = loggingparameters()))

SecondaryTrails <- secondtrailsopening(
  topography = DTMParacou,
  plotmask = PlotMask,
  maintrails = MainTrails,
  plotslope = HarvestableAreaOutputsCable$PlotSlope,
  harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
  machinepolygons = HarvestableAreaOutputsCable$MachinePolygons,
  treeselectionoutputs = treeselectionoutputs,
  scenario = scenario,
  winching = winching,
  advancedloggingparameters = loggingparameters())

usethis::use_data(SecondaryTrails, overwrite = TRUE)
```
